Glasshouse experiment

### 2018-03-13 experiment_info.Rmd
ideas intro

A common trend in natural ecosystems is pollinator sharing (REF). Therefore, pollen from different species can arrive to the stigmas of other species. The real impact of pollen in a natural ecosystem is still unknown. Nonetheless, some advances has been done with recent works where heterospecific pollen effect is evaluated (REFS).

>>>>

**Paragraph 1**
A common trend in natural ecosystems is pollinator sharing (REF). Therefore, pollen from different species can arrive to the stigmas of other species. The real impact of pollen in a natural ecosystem is still unknown. Nonetheless, some advances has been done with recent works where heterospecific pollen effect has been evaluated (REFS).

**Paragraph 2**

**Paragraph 3**

**Paragraph 4**
